THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \percent of the universe, another 
25 \percent includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in association with a single top-type quartz (tH) 
in proton-proton collisions with the CMS experiment of the LHC. The distribution of events in one of the decay channels and the 
sensitivity that we get with the current data.

@@

>>>>

There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \% of the universe, another 
25 \% includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in association with a single top-type quartz (tH) 
in proton-proton collisions with the CMS experiment of the LHC. The distribution of events in one of the decay channels and the 
sensitivity that we get with the current data. The main objective is to search for new processes such as tH Higgs production mode in the 
CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of 
adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.

Some of the objectives in this project include:
• study one or more decay channels,
• verify that simulation of signal events is adequate,
• study the extraction of signal strength through adjustments to the data,
• study the impact of statistical and systematic uncertainties.

@@

Production studies in the tH channel have already started with the collaborations CMS and ATLAS with publications based on data from the 
2011-2012 run and some data from the second run of 2015-2016. In these results it was not found signal evidence and upper limits have 
been set for the effective section. With the more sensitive analysis an upper limit is calculated for the effective section of a signal 
composed of tH and ttH that corresponds 3.1 times that expected in the SM. In this analysis the reconstruction methods do not allow to 
distinguish between tH and ttH because the effective section of ttH is much larger than that of tH and some events pass the
selections designed for tH, the fraction of tH events over tH + ttH is 5 \%. In BSM models the fraction could change up to 50 \%, for 
example with \kappa_t = -1. It could help to obtain better limits for the production of tH. The data that has been used so far 
correspond to only 20 \% of the final data of the run that which ends in 2018. The uncertainty for the signal in the current analysis is 
mostly statistical nature, therefore adding the total data in a new analysis the next year, sensitivity can be improved with an 
approximate factor of 2.2. Additionally, in subsequent phases of the LHC 2021-2023 and 2026-2038 the number of data fold and then 
multiply by 10 respectively. With these additions It is expected that the signal from the Higgs boson can be observed on the tH 
production channel. The current results can be used to project sensitivity in the third run and the high brightness phase and thus 
contribute to the planning of the updates of the detector.
